Preliminary Survey on Statistics and Software (Answers)

### 2019-09-06 static/homeworks/00-preliminary-survey-answers.Rmd
Post preliminary survey answers

---
title: "Preliminary Survey on Statistics and Software (Answers)"
author: "Ryan Safner"
date: "ECON 480 - Fall 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library("tidyverse")
```

@@

### 1. Using the following sample data:

@@

### a. Find the median.

@@

### b. Calculate the sample mean, $\bar{x}$

@@

### c. Calculate the sample standard deviation, $s$

@@

### 2. For a fair, six-sided die:

### a. What is the probability of rolling a 5?

@@

### b. What is the probability of rolling an even number?

@@

### c. What is the probability of rolling an even number or a 3?

@@

### d. If you have two fair dice, what is the probability of rolling a 6 on both dice?

@@

\clearpage

### 3. Hedge fund A earns an average rate of return of 2.5% per year with a standard deviation of 0.5%, while hedge fund B earns an average rate of return of 3.0% per year with a standard deviation of 2.0\%. Which is more unusual, Hedge fund A earning a 4.0% return or hedge fund B earning a return -1.0% return? Why?^[Hint: Standardize the two hedge funds.]

@@

\clearpage

### 4. A discrete random variable $X$ has the following pdf:

```{r, echo=FALSE, results="asis"}
tribble(
  ~x, ~`p(x)`,
  10, 0.10,
  20, 0.20,
  30, 0.30,
  40, 0.40
  ) %>%
  knitr::kable(., "latex")
```

Calculate the sample standard deviation, $s$ of $X$.

@@

\clearpage

### 5. The random variable $Y$ is normally distributed with a mean of 50 and standard deviation of 12

@@

### a. What is the $Z$-score for $Y=74$?

@@

### b. In your own words, what does this $Z$-score mean?

@@

### c. What is the probability that $Y$ takes on a value *greater* than 74?

@@

\begin{figure}
\centering
  \includegraphics{00-preliminary-survey-5c.png}
\end{figure}

```{r, echo=F, eval=F}
# used to make figure
update_geom_defaults("label", list(family = "Fira Sans Condensed"))

>>>>

---
title: "Preliminary Survey on Statistics and Software (Answers)"
author: "Ryan Safner"
date: "ECON 480 - Fall 2019"
output:
  html_document:
    df_print: kable
    theme: simplex
    toc: true 
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: tango

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
library("tidyverse")
library("kableExtra")
```

@@

## 1.
#### Using the following sample data:

@@

### a.

#### Find the median.

@@

### b.

#### Calculate the sample mean, $\bar{x}$

@@

### c. 
#### Calculate the sample standard deviation, $s$

@@

## 2.

For a fair, six-sided die:

### a.
#### What is the probability of rolling a 5?

@@

### b. 
#### What is the probability of rolling an even number?

@@

### c.
#### What is the probability of rolling an even number or a 3?

@@

### d.
#### If you have two fair dice, what is the probability of rolling a 6 on both dice?

@@

## 3.

#### Hedge fund A earns an average rate of return of 2.5% per year with a standard deviation of 0.5%, while hedge fund B earns an average rate of return of 3.0% per year with a standard deviation of 2.0\%. Which is more unusual, Hedge fund A earning a 4.0% return or hedge fund B earning a return -1.0% return? Why?^[Hint: Standardize the two hedge funds.]

@@

## 4.
#### A discrete random variable $X$ has the following pdf:

```{r, echo=FALSE, results="asis"}
tribble(
  ~x, ~`p(x)`,
  10, 0.10,
  20, 0.20,
  30, 0.30,
  40, 0.40
  ) %>%
  knitr::kable()%>%
  kable_styling()
```

#### Calculate the sample standard deviation, $s$ of $X$.

@@

## 5. 
#### The random variable $Y$ is normally distributed with a mean of 50 and standard deviation of 12

@@

### a. 
#### What is the $Z$-score for $Y=74$?

@@

### b.
#### In your own words, what does this $Z$-score mean?

@@

### c.
#### What is the probability that $Y$ takes on a value *greater* than 74?

@@

```{r, echo=F, fig.retina=3}
# used to make figure
update_geom_defaults("label", list(family = "Fira Sans Condensed"))
